Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-04 ms.tex
fixed nicks tscale definition to something more palatable

If Compton heating acts alone, i.e. $\tilde{v}_{w} = v_{w}^{C}$, then
solving equation (\ref{eq:vC}) for $\tilde{v}_{\rm w}$ yields
\begin{align} v_{w}^{\rm C} \simeq
  \begin{cases} 140 \eta_{0.02}^{0.21}T_{\rm
C,9}^{0.21}\epsilon_{-2}^{0.21} M_{\bullet,8}^{0.16}\,{\rm km\,s^{-1}}
&, \text{core}\\ 95 \eta_{0.02}^{0.34}T_{\rm
C,9}^{0.29}\epsilon_{-2}^{0.29} M_{\bullet,8}^{0.14}\,{\rm km\,s^{-1}}
&, \text{cusp},
  \end{cases}
  \label{eq:vC2}
\end{align} 
Compton heating can thus be significant in young stellar populations
with relatively high mass loss rates, e.g. $v_{w}^{\rm C} \gtrsim 300$
km s$^{-1}$ for $\eta \gtrsim 1$.  The mass accretion rate
corresponding to the state where Compton heating limits the average
accretion rate is given by substituting equation (\ref{eq:vC2}) into
equation (\ref{eq:eddr_analytic}):
\begin{align}
\frac{\dot{M}_{C}}{\dot{M}_{\rm edd}} \approx 
\begin{cases} 2\times 10^{-3} \eta_{0.02}^{0.2}T_{\rm
C,9}^{-0.8}\epsilon_{-2}^{-0.8} M_{\bullet,8}^{0.16}
&, \text{core}\\ 8\times 10^{-4} \eta_{0.02}^{0.3}T_{\rm
C,9}^{-0.7}\epsilon_{-2}^{-0.7} M_{\bullet,8}^{0.14}
&, \text{cusp},
  \end{cases}
  \label{eq:MdotCa}
\end{align}
If the accretion luminosity $\epsilon = 10 \dot{M}/\dot{M}_{\rm edd}$
depends on the Eddington ratio as predicted by some models for
radiatively inefficient accretion flows (\citealt{Narayan&Yi95};
\citealt{Narayan+98}; \citealt{XieYuan:2012a}), then the Compton-limited accretion rate becomes
\begin{align}
\frac{\dot{M}_{C}}{\dot{M}_{\rm edd}} \approx 
\begin{cases} 1.7\times 10^{-2} \eta_{0.02}^{0.12}T_{\rm
C,9}^{-0.44}M_{\bullet,8}^{0.09}
&, \text{core}\\ 8.6\times 10^{-4} \eta_{0.02}^{0.17}T_{\rm
C,9}^{-0.4} M_{\bullet,8}^{0.08}
&, \text{cusp}.
  \end{cases}
  \label{eq:MdotC}
\end{align}
%{\bf  Total efficiency is 10 (mdot/MdotEdd). Everywhere.}

@@

Assume that the outflow power is proportional to the SMBH accretion rate, $L_{\rm j} =
\epsilon_{\rm j} \dot{M}c^{2}$, where $\epsilon_{\rm j} < 1$ is a jet efficiency factor.  Further assume that this energy is deposited as heat uniformly interior to a radius $r_{\rm heat}$ and volume $V_{\rm heat} \propto r_{\rm
heat}^{3}$.  The resulting volumetric heating rate $e = \epsilon_{\rm
j}\dot{M}c^{2}/V_{\rm heat}$ near the stagnation radius results in a heating parameter given by
\begin{eqnarray} v_{w}^{\bullet} &\approx& \left(\frac{2t_{\rm
h}\epsilon_{\rm j}\dot{M}c^{2}}{V_{\rm heat}\eta
\rho_{\star}|_{r_{s}}}\right)^{1/2} \sim \left(\frac{\epsilon_{\rm
j}\dot{M}c^{2}t_{\rm h}}{\eta M_{\rm enc}}\right)^{1/2} \nonumber \\
&\approx& 300\,{\rm km\,s^{-1}}\,\left(\frac{\epsilon_{\rm j}}{10^{-6}}\right)^{1/2}\left(\frac{r_{\rm s}}{r_{\rm
heat}}\right)^{1-\Gamma/2},
\label{eq:vjet}
\end{eqnarray} 
where we have used the facts that $\dot{M} = \eta M_{\star}|_{r_{\rm s}}/t_{\rm h}$ and, for radii inside the Nuker break radius, $M_{\star}(r) \propto
M_{\bullet}(r/r_{\rm soi})^{2-\Gamma}$ (eq.~[\ref{eq:rhostar}]).  If the bulk of the outflow energy is released near the stagnation radius, then even a small heating efficiency $\epsilon_{\rm j} \gtrsim
10^{-5}$ is sufficient for $v_{w}^{\bullet}$ to exceed other sources of non-accretion powered heating.  However, if this energy is instead deposited over much larger physical scales comparable to the size of the galaxy, i.e. $r_{\rm heat} \gtrsim $ 10 kpc $\sim 10^{4}r_{\rm s}$, then kinetic feedback is unimportant, even for a powerful jet with $\epsilon_{\rm j} \sim 1$.

Using the results of \citet{Bromberg+11}, the time required for a jet of luminosity $L_{\rm
  j}$ and half opening angle $\theta_{\rm j} = 0.1$ (characteristic of
AGN jets) to propagate through a gaseous mass $M_{\rm g}$ of radius $r$ is estimated to be
\begin{eqnarray}
t_{\rm jet} &\sim& 4000\,{\rm yr}\left(\frac{{L}_{\rm j}}{10^{40}\,\rm erg\,s^{-1}}\right)^{-1/3}\left(\frac{r}{\rm pc}\right)^{2/3}\left(\frac{M_{\rm g}}{10^{8}M_{\odot}}\right)^{1/3} 
\end{eqnarray}
Approximating $M_{\rm g} \sim \dot{M}t_{\rm ff}$, the ratio of the jet escape timescale to the dynamical timescale $t_{\rm dyn} \sim r/\sigma$ is given by
\begin{equation}
\frac{t_{\rm jet}}{t_{\rm dyn}} \sim 7\times 10^{-3}M_{\bullet,8}^{0.13}\left(\frac{\epsilon_{\rm j}}{10^{-6}}\right)^{-1/3},
\end{equation}
independent of $r$.  A jet with power sufficient to appreciably heat
the CNM on radial scales $\sim r_{\rm s}$ ($\epsilon_{j} \gtrsim
10^{-6}$) also necessarily has sufficient power to escape the nuclear
region and propagate to much larger radii.  Slower outflows from the
accretion disk, instead of a collimated relativistic jet, may provide
a more promising source of feedback in these systems
(e.g.~\citealt{Li+13}).

@@

Figure~\ref{fig:vwSourcesImp} shows the contributions of various heating sources as a function of time $\tau_{\star}$ after a burst of star formation for black holes of mass $\Mbh = 10^{6} \Msun$ (top panel) and $\Mbh = 10^{8} \Msun$ (bottom panel). The heating and mass input parameters due to stellar winds, $v_{w}^{\star}(\tau_{\star})$ and $\eta(\tau_{\star})$, are calculated as described in Appendix~\ref{app:windheat} (Fig.~\ref{fig:vwImp}).  The heating from SN Ia ($v_{w}^{\rm Ia}$) and Compton heating ($v_{\rm w}^{\rm C}$) are calculated from equations~\eqref{eq:vIa} and~\eqref{eq:vC} respectively, also making use of $\eta(\tau_{\star})$ from stellar winds.  SN Ia heating depends also on a convolution of the DTD (eq. [\ref{eq:DTD}]) and the star formation history, which reduces to the DTD itself for a single star burst.  {\bf BDM: do we even include Ia heating?}

We crudely account for the expected suppression of SN Ia heating resulting from its non-steady nature by attenuating $v_{w}^{\rm Ia}$ by a factor $e^{-\rs/\rIa}$, where $r_{\rm Ia}$ is the radius exterior to which the time between subsequent supernovae exceeds the local dynamical time (eq.~[\ref{eq:rIa}]).  Finally, note that $v_{\rm w}^{\rm C}$ and $v_{\rm w}^{\rm Ia}$ also depend on the total heating rate (eq.~[\ref{eq:vtot}]), requiring us to simultaneously solve a series of implicit equations to determine each heating rate.  Heating from MSPs is found to be negligibly small for fiducial parameters and hence is not shown, while kinetic feedback is neglected given its uncertain efficiency ($\S\ref{sec:kinetic}$).

@@

Realistic variations (``burstiness") in the star formation history
will often result in lower heating rates.  Figure \ref{fig:NickPlot2}
shows the heating rate as a function of average black hole mass for
non-fiducial cases in which the current ($z = 0$) star formation is
suppressed by a factor $\iota$ from its average $z = 0$ value, for a
characteristic timescale $t_{\rm scale}$ (for details, see Appendix
\ref{app:windheat}).  For $t_{\rm scale} \lesssim 10^{7}$ yr, we see
that $v_{\rm w}^{\star}$ is reduced by at most a factor of $\approx 2$
from its average value, even for huge drops in the star formation rate
($\iota \sim 10^{-3}$).  However, burstiness in the star formation
history over longer timescales can suppress heating more
significantly.  When $t_{\rm scale} \gtrsim 10^8~{\rm yr}$, $v_{\rm
  w}^\star$ becomes very sensitive to $\iota$: at $\iota=0.1$, $v_{\rm
  w}^\star \approx 500~{\rm km~s}^{-1}$ in most galaxies, but for
smaller $\iota$, $v_{\rm w}^\star \approx 200~{\rm km~s}^{-1}$ (an
exception to this is in galactic nuclei with $M_\bullet \gtrsim
5\times 10^8~M_\odot$, where heating is stabilized by SN Ia).  Our use
of average cosmic star formation histories is appropriate provided
local variations are either on short timescales ($t_{\rm scale}
\lesssim 10^7~{\rm yr}$), or limited in magnitude ($\iota \gtrsim
0.1$).  If both of these conditions are violated, then the effective
heating rates for all but the most massive galaxies (where Ia
explosions dominate) will fall by a factor $\approx 5$ from our
fiducial volumetric averages, taken from \citet{MosterNaab+:2013a}.

>>>>

If Compton heating acts alone, i.e. $\tilde{v}_{w} = v_{w}^{C}$, then
solving equation (\ref{eq:vC}) for $\tilde{v}_{\rm w}$ yields
\begin{align} v_{w}^{\rm C} \simeq
  \begin{cases} 140 \eta_{0.02}^{0.21}T_{\rm
C,9}^{0.21}\epsilon_{-2}^{0.21} M_{\bullet,8}^{0.16}\,{\rm km\,s^{-1}}
&, \text{core}\\ 95 \eta_{0.02}^{0.34}T_{\rm
C,9}^{0.29}\epsilon_{-2}^{0.29} M_{\bullet,8}^{0.14}\,{\rm km\,s^{-1}}
&, \text{cusp},
  \end{cases}
  \label{eq:vC2}
\end{align} 
Compton heating can thus be significant in young stellar populations
with relatively high mass loss rates, e.g. $v_{w}^{\rm C} \gtrsim 300$
km s$^{-1}$ for $\eta \gtrsim 1$.  The accretion rate
corresponding to a state in which Compton heating self-regulates the accretion flow is given by substituting equation (\ref{eq:vC2}) into equation (\ref{eq:eddr_analytic}):
\begin{align}
\frac{\dot{M}_{C}}{\dot{M}_{\rm edd}} \approx 
\begin{cases} 2\times 10^{-3} \eta_{0.02}^{0.2}T_{\rm
C,9}^{-0.8}\epsilon_{-2}^{-0.8} M_{\bullet,8}^{0.16}
&, \text{core}\\ 8\times 10^{-4} \eta_{0.02}^{0.3}T_{\rm
C,9}^{-0.7}\epsilon_{-2}^{-0.7} M_{\bullet,8}^{0.14}
&, \text{cusp}.
  \end{cases}
  \label{eq:MdotCa}
\end{align}
If the accretion luminosity $\epsilon = 10 \dot{M}/\dot{M}_{\rm edd}$ depends on the Eddington ratio as predicted by some models for
radiatively inefficient accretion flows (\citealt{Narayan&Yi95};
\citealt{Narayan+98}; \citealt{XieYuan:2012a}), then the Compton-limited accretion rate becomes
\begin{align}
\frac{\dot{M}_{C}}{\dot{M}_{\rm edd}} \approx 
\begin{cases} 1.7\times 10^{-2} \eta_{0.02}^{0.12}T_{\rm
C,9}^{-0.44}M_{\bullet,8}^{0.09}
&, \text{core}\\ 8.6\times 10^{-4} \eta_{0.02}^{0.17}T_{\rm
C,9}^{-0.4} M_{\bullet,8}^{0.08}
&, \text{cusp}.
  \end{cases}
  \label{eq:MdotC}
\end{align}
We note that accretion is unlikely to be steady in cases where AGN heating dominates, due to the inherent delay between black hole feedback and the structure of the accretion flow on larger scales.  
%{\bf  Total efficiency is 10 (mdot/MdotEdd). Everywhere.}

@@

Assume that the outflow power is proportional to the SMBH accretion rate, $L_{\rm j} =
\epsilon_{\rm j} \dot{M}c^{2}$, where $\epsilon_{\rm j} < 1$ is a jet efficiency factor.  Further assume that this energy is deposited as heat uniformly interior to a radius $r_{\rm heat}$ and volume $V_{\rm heat} \propto r_{\rm
heat}^{3}$.  The resulting volumetric heating rate $e = \epsilon_{\rm
j}\dot{M}c^{2}/V_{\rm heat}$ near the stagnation radius results in a heating parameter given by
\begin{eqnarray} v_{w}^{\bullet} &\approx& \left(\frac{2t_{\rm
h}\epsilon_{\rm j}\dot{M}c^{2}}{V_{\rm heat}\eta
\rho_{\star}|_{r_{s}}}\right)^{1/2} \sim \left(\frac{\epsilon_{\rm
j}\dot{M}c^{2}t_{\rm h}}{\eta M_{\rm enc}}\right)^{1/2} \nonumber \\
&\approx& 300\,{\rm km\,s^{-1}}\,\left(\frac{\epsilon_{\rm j}}{10^{-6}}\right)^{1/2}\left(\frac{r_{\rm s}}{r_{\rm
heat}}\right)^{1-\Gamma/2},
\label{eq:vjet}
\end{eqnarray} 
where we have used the facts that $\dot{M} = \eta M_{\star}|_{r_{\rm s}}/t_{\rm h}$ and, for radii inside the Nuker break radius, $M_{\star}(r) \propto
M_{\bullet}(r/r_{\rm soi})^{2-\Gamma}$ (eq.~[\ref{eq:rhostar}]).  If the bulk of the outflow energy is released near the stagnation radius, then even a small heating efficiency $\epsilon_{\rm j} \gtrsim
10^{-5}$ is sufficient for $v_{w}^{\bullet}$ to exceed other sources of non-accretion powered heating.  However, if this energy is instead deposited over much larger physical scales comparable to the size of the galaxy, i.e. $r_{\rm heat} \gtrsim $ 10 kpc $\sim 10^{4}r_{\rm s}$, then kinetic feedback is unimportant, even for a powerful jet with $\epsilon_{\rm j} \sim 0.1$.

The time required for a jet of luminosity $L_{\rm
  j}$ and half opening angle $\theta_{\rm j} = 0.1$ (characteristic of
AGN jets) to propagate through a gaseous mass $M_{\rm g}$ of radius $r$ is estimated from \citet{Bromberg+11} to be 
\begin{eqnarray}
t_{\rm jet} \sim 4000\,{\rm yr}\left(\frac{{L}_{\rm j}}{10^{40}\,\rm erg\,s^{-1}}\right)^{-1/3}\left(\frac{r}{\rm pc}\right)^{2/3}\left(\frac{M_{\rm g}}{10^{8}M_{\odot}}\right)^{1/3} 
\end{eqnarray}
Approximating $M_{\rm g} \sim \dot{M}t_{\rm ff}$, the ratio of the jet escape timescale to the dynamical timescale $t_{\rm dyn} \sim r/\sigma$ is given by
\begin{equation}
\frac{t_{\rm jet}}{t_{\rm dyn}} \sim 7\times 10^{-3}M_{\bullet,8}^{0.13}\left(\frac{\epsilon_{\rm j}}{10^{-6}}\right)^{-1/3},
\end{equation}
independent of $r$.  A jet with power sufficient to appreciably heat
the CNM on radial scales $\sim r_{\rm s}$ ($\epsilon_{j} \gtrsim
10^{-6}$) also necessarily has sufficient power to escape the nuclear
region and propagate to much larger radii.  Slower outflows from the
accretion disk, instead of a collimated relativistic jet, may provide
a more promising source of feedback in these systems
(e.g.~\citealt{Li+13}).

@@

Figure~\ref{fig:vwSourcesImp} shows the contributions of various heating sources as a function of time $\tau_{\star}$ after a burst of star formation for black holes of mass $\Mbh = 10^{6} \Msun$ (top panel) and $\Mbh = 10^{8} \Msun$ (bottom panel). The heating and mass input parameters due to stellar winds, $v_{w}^{\star}(\tau_{\star})$ and $\eta(\tau_{\star})$, are calculated as described in Appendix~\ref{app:windheat} (Fig.~\ref{fig:vwImp}).  The heating from SN Ia ($v_{w}^{\rm Ia}$) and Compton heating ($v_{\rm w}^{\rm C}$) are calculated from equations~\eqref{eq:vIa} and~\eqref{eq:vC} respectively, also making use of $\eta(\tau_{\star})$ from stellar winds.  SN Ia heating depends also on a convolution of the DTD (eq. [\ref{eq:DTD}]) and the star formation history, which reduces to the DTD itself for a single star burst.

We crudely account for the expected suppression of SN Ia heating resulting from its non-steady nature by setting $v_{w}^{\rm Ia} = 0$ when the stagnation radius (calculated excluding Ia heating) exceeds the Ia radius $r_{\rm Ia}$ exterior to which the interval between subsequent supernovae exceeds the local dynamical time (eq.~[\ref{eq:rIa}]).  Finally, note that $v_{\rm w}^{\rm C}$ and $v_{\rm w}^{\rm Ia}$ also depend on the total heating rate (eq.~[\ref{eq:vtot}]), requiring us to simultaneously solve a series of implicit equations to determine each heating rate.  Heating from MSPs is found to be negligibly small for fiducial parameters and hence is not shown, while kinetic feedback is neglected given its uncertain efficiency ($\S\ref{sec:kinetic}$).

@@

Realistic variations (``burstiness") in the star formation history
will often result in lower heating rates.  Figure \ref{fig:NickPlot2}
shows the heating rate as a function of average black hole mass for
non-fiducial cases in which the current ($z = 0$) star formation is
suppressed by a factor $\iota$ from its average $z = 0$ value, for a
characteristic timescale $\delta t_{\star}$ (for details, see Appendix
\ref{app:windheat}).  For $t_{\rm scale} \lesssim 10^{7}$ yr, we see
that $v_{\rm w}^{\star}$ is reduced by at most a factor of $\approx 2$
from its average value, even for huge drops in the star formation rate
($\iota \sim 10^{-3}$).  However, burstiness in the star formation
history over longer timescales can suppress heating more
significantly.  When $t_{\rm scale} \gtrsim 10^8~{\rm yr}$, $v_{\rm
  w}^\star$ becomes very sensitive to $\iota$: at $\iota=0.1$, $v_{\rm
  w}^\star \approx 500~{\rm km~s}^{-1}$ in most galaxies, but for
smaller $\iota$, $v_{\rm w}^\star \approx 200~{\rm km~s}^{-1}$ (an
exception to this is in galactic nuclei with $M_\bullet \gtrsim
5\times 10^8~M_\odot$, where heating is stabilized by SN Ia).  Our use
of average cosmic star formation histories is appropriate provided
local variations are either on short timescales ($t_{\rm scale}
\lesssim 10^7~{\rm yr}$), or limited in magnitude ($\iota \gtrsim
0.1$).  If both of these conditions are violated, then the effective
heating rates for all but the most massive galaxies (where Ia
explosions dominate) will fall by a factor $\approx 5$ from our
fiducial volumetric averages, taken from \citet{MosterNaab+:2013a}.

### 2015-04-04 windheat.tex
references.
fixed nicks tscale definition to something more palatable

The effective wind velocity in the limit of an impulsive star formation may then be written
as 
\begin{align}
\bar{v}_w(t)=2 \dot{\bar{e}}(t)/\dot{\bar{m}}(t)
\label{eq:vwImp}
\end{align}
while 
\begin{align}
\eta = \dot{\bar{m}}(t) \th
\label{eq:vwImp}
\end{align}
 Figur~\ref{fig:vwImp} shows the values of $\bar{v}_w(t)$ and $\eta(t)$ as a function of stellar age, $\tau_{\star}$.

@@

 \begin{figure}
  \includegraphics[width=\columnwidth]{NickPlot2.pdf}
  \caption{\label{fig:NickPlot2} Effective wind velocities for nonstandard
    star formation histories.  The black curve shows, for reference,
    $v_{\rm w}$ calculated using the halo-averaged $S(t)$.  Other
    colors show the effective wind velocities $\mathcal{V}_{\rm w}$
    computed using convolved star formation histories
    $\mathcal{S}(t)$.  The purple curve shows a recent drop in the
    star formation rate, i.e. $t_{\rm scale}=10^6~{\rm yr}$.  The blue
    and red curves show $t_{\rm scale}=10^7~{\rm yr}$ and $t_{\rm
      scale}=10^8~{\rm yr}$, respectively; longer scale times look
    quite similar to the red curves.  Dashed, dotted, and dot-dashed
    line styles show star formation rates that have declined to
    fractions $\iota= 0.001$, $\iota = 0.1$, and $\iota = 0.3$ of
    their halo-averaged values, respectively. }
  \end{figure}
  We estimate the stellar wind heating provided by the {\it average}
  star formation history of galaxies of a given $\Mbh$ using the
  results of \citet[eqs.~17-20]{MosterNaab+:2013a}.  Note that the
  star formation histories in \citet{MosterNaab+:2013a} are in terms
  of halo mass. For a given $\Mbh$ we assign the halo mass whose star
  formation history would produce a bulge consistent with the
  $\Mbh-M_{\rm bulge}$ relationship from \citet{McConnellMa:2013a}.  A
  slight complication occurs for the largest mass halos, where much of
  the $z=0$ stellar mass has been acquired through accretion of
  satellite halos rather than {\it in situ} star formation.  To
  accomodate this, we incorporate analytic fits for mass accretion
  histories, taken from \citet[their eqs.~21-23]{MosterNaab+:2013a},
  assuming that the age distribution of the accreted stars is equal to
  the age distribution of those formed {\it in situ}.  This assumption
  may be conservative if the primary galaxy's accretion history is
  dominated by minor mergers with younger stellar populations.  On the
  other hand, the dynamical friction inspiral time for small satellite
  galaxies is quite long, generally much greater than the $\sim
  10^7~{\rm yr}$ for which young stars can dominate the heating
  budget.

@@

Figure \ref{fig:NickPlot2} shows how the wind heating varies as star formation histories deviate from their halo-averaged values.  In particular, we show
\begin{align} 
  \dot{\mathcal{M}}(t) &= \int_0^t \mathcal{S}(t_1) \dot{\bar{m}}(t-t_1){\rm
      d}t_1\\
  \dot{\mathcal{E}}(t) &= \int_0^t \mathcal{S}(t_1) \dot{\bar{e}}(t-t_1){\rm
      d}t_1,\\
  \mathcal{V}_w^2(t) &=2 \dot{\mathcal{E}}(t)/\dot{\mathcal{M}}(t).
\end{align}
In these equations, 
\begin{equation}
\mathcal{S}(t) = S(t) \times \left(\frac{2}{\pi}(1-\iota)\arctan(t/t_{\rm scale}) + \iota \right).
\end{equation}
This function convolves the recent ($z \approx 0$) halo-averaged star formation history with local variation to give a more pessimistic estimate for the value of $\tilde{v}_{\rm w}$.  In particular, replacing $S(t)$ with $\mathcal{S}(t)$ reduces the recent star formation rate to a fraction $\epsilon$ of its halo-averaged value, and does so for a characteristic time $t_{\rm scale}$ into the past.  As we can see in Fig. \ref{fig:NickPlot2}, this dramatically lowers the effective wind speed when both $t_{\rm scale} \gtrsim 10^7 ~{\rm yr}$ and $\epsilon \lesssim 0.1$, but otherwise has too modest of an effect to change the thermal stability properties of the flow (although the location of $r_{\rm s}$ and the value of $\dot{M}$ may change significantly).

>>>>

The effective wind velocity in the limit of an impulsive star formation may then be written
as 
\begin{align}
\bar{v}_w(t)=2 \dot{\bar{e}}(t)/\dot{\bar{m}}(t)
\label{eq:vwImp}
\end{align}
while 
\begin{align}
\eta = \dot{\bar{m}}(t) \th
\label{eq:etaImp}
\end{align}
 Figure~\ref{fig:vwImp} shows the values of $\bar{v}_w(t)$ and $\eta(t)$ as a function of stellar age, $\tau_{\star}$.

@@

 \begin{figure}
  \includegraphics[width=\columnwidth]{NickPlot2.pdf}
  \caption{\label{fig:NickPlot2} Effective wind velocities for nonstandard
    star formation histories.  The black curve shows, for reference,
    $v_{\rm w}$ calculated using the halo-averaged $S(t)$.  Other
    colors show the effective wind velocities $\mathcal{V}_{\rm w}$
    computed using convolved star formation histories
    $\mathcal{S}(t)$.  The purple curve shows a recent drop in the
    star formation rate, i.e. $\delta t_{\star}=10^6~{\rm yr}$.  The blue
    and red curves show $\delta t_{\star}=10^7~{\rm yr}$ and $t_{\rm
      scale}=10^8~{\rm yr}$, respectively; longer scale times look
    quite similar to the red curves.  Dashed, dotted, and dot-dashed
    line styles show star formation rates that have declined to
    fractions $\iota= 0.001$, $\iota = 0.1$, and $\iota = 0.3$ of
    their halo-averaged values, respectively. }
  \end{figure}
  We estimate the stellar wind heating provided by the {\it average}
  star formation history of galaxies of a given $\Mbh$ using the
  results of \citet[eqs.~17-20]{MosterNaab+:2013a}.  Note that the
  star formation histories in \citet{MosterNaab+:2013a} are in terms
  of halo mass. For a given $\Mbh$ we assign the halo mass whose star
  formation history would produce a bulge consistent with the
  $\Mbh-M_{\rm bulge}$ relationship from \citet{McConnellMa:2013a}.  A
  slight complication occurs for the largest mass halos, where much of
  the $z=0$ stellar mass has been acquired through accretion of
  satellite halos rather than {\it in situ} star formation.  To
  accomodate this, we incorporate analytic fits for mass accretion
  histories, taken from \citet[their eqs.~21-23]{MosterNaab+:2013a},
  assuming that the age distribution of the accreted stars is equal to
  the age distribution of those formed {\it in situ}.  This assumption
  may be conservative if the primary galaxy's accretion history is
  dominated by minor mergers with younger stellar populations.  On the
  other hand, the dynamical friction inspiral time for small satellite
  galaxies is quite long, generally much greater than the $\sim
  10^7~{\rm yr}$ for which young stars can dominate the heating
  budget.

@@

Figure \ref{fig:NickPlot2} shows how the wind heating varies as star formation histories deviate from their halo-averaged values.  In particular, we show
\begin{align} 
  \dot{\mathcal{M}}(t) &= \int_0^t \mathcal{S}(t_1) \dot{\bar{m}}(t-t_1){\rm
      d}t_1\\
  \dot{\mathcal{E}}(t) &= \int_0^t \mathcal{S}(t_1) \dot{\bar{e}}(t-t_1){\rm
      d}t_1,\\
  \mathcal{V}_w^2(t) &=2 \dot{\mathcal{E}}(t)/\dot{\mathcal{M}}(t).
\end{align}
In these equations, 
\begin{equation}
\mathcal{S}(t) = S(t) \times \left(\frac{2}{\pi}(1-\iota)\arctan(t/\delta t_{\star}) + \iota \right).
\end{equation}
This function convolves the recent ($z \approx 0$) halo-averaged star formation history with local variation to give a more pessimistic estimate for the value of $\tilde{v}_{\rm w}$.  In particular, replacing $S(t)$ with $\mathcal{S}(t)$ reduces the recent star formation rate to a fraction $\epsilon$ of its halo-averaged value, and does so for a characteristic time $\delta t_{\star}$ into the past.  As we can see in Fig. \ref{fig:NickPlot2}, this dramatically lowers the effective wind speed when both $\delta t_{\star} \gtrsim 10^7 ~{\rm yr}$ and $\epsilon \lesssim 0.1$, but otherwise has too modest of an effect to change the thermal stability properties of the flow (although the location of $r_{\rm s}$ and the value of $\dot{M}$ may change significantly).
